\chapter{Results}

\section{Traffic Volume Counting}

This section of the results documents the performance of the computer vision algorithm for counting vehicles that use the road observed by a camera node. Each table refers to a specific traffic setting and more detailed descriptions and images of each traffic setting may be found in Appendix C.1. \cite{udacity_cv} DUMMY REFERENCE

\begin{itemize}
\item\textbf{Location} is simply an identifying number for a traffic setting. Further information for each setting can be found in Appendix \ref{appendices:traffic_descriptors}.
\item\textbf{Lane} refers to the direction of traffic that is being measured. It may be up/down or left/right.
\item\textbf{True Positive} means that a vehicle was present and correctly identified and counted (TP).
\item\textbf{False Positive} means that a vehicle was not present but one was counted anyway (FP).
\item\textbf{False Negative} means that a vehicle was present but the algorithm failed to count it (FN).
\item\textbf{True Count} is the actual number of vehicles that passed the camera node. 
\item\textbf{Precision} is the proportion of positive classifications that are actually correct, where \[Precision = \frac{TP}{TP + FP}\]
\item\textbf{Recall} is the proportion of actual positives that were correctly identified, where \[Recall = \frac{TP}{TP + FN}\]
\item\textbf{F1} is the harmonic mean of the precision and recall of the algorithm, where \[F1 = \frac{2(precision \centerdot recall)}{precision + recall}\]
\item\textbf{Accuracy} is the ratio of the true positives to the number of actual positives, where \[Accuracy = \frac{TP}{True Count}\]
\end{itemize}



\begin{table}[H]
    \centering
    \begin{tabular}{|cccccccccc|} 
    \hline
    \textbf{Location} & \textbf{Lane} & \textbf{FP} & \textbf{FN}& \textbf{TP}& \textbf{True Count}&\textbf{Precision}& \textbf{Recall}& \textbf{Accuracy} & \textbf{F1}\\
    \hline
    \multirow{3}{4em}{1}  
    &Up&0&5&41&46&100.00\%&89.13\%&89.13\%&94.25\%\\\cline{2-10}
    &Down&0&3&55&58&100.00\%&94.83\%&94.83\%&97.35\%\\\cline{2-10}
    &Total&0&8&96&104&100.00\%&92.31\%&92.31\%&96.00\%\\\Xhline{1pt}

    \multirow{3}{4em}{2}
    &Up&-&-&-&-&-&-&-&-\\\cline{2-10}
    &Down&1&4&61&65&98.39\%&93.85\%&91.18\%&96.06\%\\\cline{2-10}
    &Total&1&4&61&65&98.39\%&93.85\%&91.18\%&96.06\%\\\Xhline{1pt}

    \multirow{3}{4em}{3}
    &Up&1&3&38&41&97.44\%&92.68\%&92.68\%&95.00\%\\\cline{2-10}
    &Down&2&2&38&39&95.00\%&95.00\%&97.44\%&95.00\%\\\cline{2-10}
    &Total&3&5&76&80&96.20\%&93.38\%&95.00\%&95.00\%\\\Xhline{1pt}

    \multirow{3}{4em}{4}
    &Up&1&3&38&41&97.44\%&92.68\%&92.68\%&95.00\%\\\cline{2-10}
    &Down&2&2&38&39&95.00\%&95.00\%&97.44\%&95.00\%\\\cline{2-10}
    &Total&3&5&76&80&96.20\%&93.38\%&95.00\%&95.00\%\\\Xhline{1pt}


    
\end{tabular}
\caption{Traffic Volume Count Evaluation Metrics}
\end{table}
\raggedbottom

\section{Speed Measurements}

[INSERT SPEED MEASUREMENT TABLES]

[INSERT DISCUSSION OF RESULTS]

